Data Exploration

### 2018-11-26 src/data_exploration.Rmd
correlation plots of presence NB output is effectively non-readable

>>>>

## correlations between background points

check to see if there are any correlations in the env. variables

first subset the env.correlate columns (you don't need everything)

```{r}
str(background)
background_env <- subset(background, select = c(amo_sample, amo_winter, amo_prev, nao_sample, nao_winter, nao_prev, chl_surface, chl_depth, mlp_surface, ssh_surface, temp_surface, temp_depth, o2_surface, o2_depth, salinity_surface, salinity_depth))
dev.copy(png, "../output/env/simple_plots/background_corr.png") # to automatically save the plot to a png AND show it inline
backpairs <- pairs(background_env)
dev.copy(png, "../output/env/simple_plots/background_corr.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png
```

## correlations between presence points

check to see if there are any correlations in the env. variables

first subset the env.correlate columns (you don't need everything)

```{r}
str(presence)
pres_env <- subset(presence, select = c(amo_sample, amo_winter, amo_prev, nao_sample, nao_winter, nao_prev, chl_surface, chl_depth, mlp_surface, ssh_surface, temp_surface, temp_depth, o2_surface, o2_depth, salinity_surface, salinity_depth))
png("../output/env/simple_plots/presence_corr.png") # to automatically save the plot to a png AND show it inline
pairs(pres_env)
dev.off() # stops automatic saving of the plot to a png
```
